\subsection{How We Worked as a Team}
In order to facilitate and improve the efficiency of teamwork within our group, we made use of several tools and strategies throughout the semester. For communication within the group, we used the Slack messaging app. For collaboration on code, we made use of git for version control, and github for code reviews. Weekly in-person meetings were had amongst all team members in order to come with fresh project ideas as a group, and to ensure that all of us were on the same page. Weekly in-person meetings with our supervisor were also had for similar reasons, and to ensure that we stayed on track throughout the year. Without the use of these tools and strategies, the development process for this project would have been much more difficult.

\subsection{Individual Contributions}
Below we show the individual contributions of each person. Note, however, that much work was done as a group, so there are many areas that were worked on collectively by everyone.

\subsubsection{Ege}
\begin{itemize}
  \item Responsible for all database and remote computing aspects of the project
  \item Built the majority of the scrapers used to collect the data
  \item Designed the database schema for housing the data
  \item Set up the remote computing environment with Paperspace
\end{itemize}

\subsubsection{Stephen}
\begin{itemize}
  \item Coded the system for computing player scores and updating database
  \item Created constraints for, and wrote the code for, the linear programming constraint solver (system 3)
  \item Added ability for system 3 to output multiple lineups
\end{itemize}
\subsubsection{Florence}
\begin{itemize}
  \item Built first prototype of neural network to predicts winning team
  \item Built second prototype of neural network for predicting player game scores
  \item Handled the creation of inputs from raw data
  \item Performed cross-validation on the network
  \item Built function to connect systems and output a lineup with Asher
\end{itemize}
\subsubsection{Asher}
\begin{itemize}
  \item Worked on scripts to compute player scores, and scripts to connect tables in the database
  \item Worked on data retrieval code from database to obtain data in a format appropriate for the neural network.
  \item Helped to implement scrapers for some player statistics
  \item Built function to process daily competition rules
  \item Built function to connect systems and output a lineup with Florence
\end{itemize}

\subsection{Evaluation of Teamwork and Difficulties}
The four of us worked very well together as a team and did not run into any major issues. We plan to continue working together on this project through the summer, and have a superior product for the next NBA season.