%-------------------------------------------------------------------
% Conclusion:
% Use this section to summarize what was accomplished in this semester, provide a summary of the next steps and share any insight you have learned.
%-------------------------------------------------------------------
The first half of our design project has been a success. Although we have not yet created a full solution to the problem of picking winning lineups for daily fantasy basketball competitions with machine learning, we are on track to do so with enough time to test and reiterate on our design. We were able to gather a sufficient amount of data to train and test a first prototype that was able to predict the outcome of a basketball game. We also found that we were able to increase the success rate of this prototype by adjusting ML parameters, by increasing the amount of data used for training, and by altering the fixtures to be more meaningful. Our best version was able to successfully predict the outcome of NBA games with 71\% accuracy. As the ultimate goal of our project is to be able to generate lineups, and not to predict the outcome of games, we still have work to do. We will have to change the NN to output the players' game scores, and then subsequently create a system to take in these game scores, the cost of each player, and the lineup budget, and output optimal lineups. After doing this, we will have to test our system, and improve certain aspects of it, such as how we obtain player scores. The end result will hopefully be a working and well-tested system that is able to generate profitable lineups for fantasy basketball competitions.