%TODO get references all in the same format
\begin{thebibliography}{9}
\bibitem{energy} 
"How much of U.S. energy consumption and electricity generation comes from renewable energy sources?", U.S. Energy Information Administration, 2017. [Online]. Available: https://www.eia.gov/tools/faqs/faq.php?id=92.

%TODO find first name
\bibitem{neural_net} 
Karpathy, "Convolutional Neural Networks for Visual Recognition", Stanford. [Online]. Available: http://cs231n.github.io/neural-networks-1/.

\bibitem{caltech} 
Abu-Mostafa, Yaser. "Learning From Data", Caltech, 2012. [Online]. Available: https://work.caltech.edu/telecourse.

\bibitem{neural_net_fundies} 
"A Basic Introduction To Neural Networks", University of Wisconsin-Madison. [Online]. Available: http://pages.cs.wisc.edu/~bolo/shipyard/neural/local.html.


\bibitem{picking_winners}
Hunter, David Scott, et al. “Picking Winners Using Integer Programming.” \textit{ArXiv:1604.01455 [Stat.OT]}, 6 July 2016.

\bibitem{GPU}
Kaminski, J. (2009). "How much power does your video card use?." CNET. Available: https://www.cnet.com/news/how-much-power-does-your-video-card-use/.

\bibitem{iphone}
Mayo, B. (2015). iPhone 6s Plus battery rated 2750 mAH, 5\% smaller capacity than iPhone 6 Plus. 9to5Mac. Available: https://9to5mac.com/2015/09/21/phone-6s-plus-smaller-battery/.

\bibitem{fantasyQuantity}
Kounang, N. (2016, March 18). Inside the brains of bros on fantasy sports. Retrieved April 17, 2018, from https://www.cnn.com/2016/03/18/health/fantasy-sports-psychology/index.html

\bibitem{fantasySportsTimeSpent}
YouGov. "How Much Time Do You Spend on Managing Your Fantasy Football Team?*." Statista - The Statistics Portal, Statista, www.statista.com/statistics/284718/amount-of-time-spent-on-managing-fantasy-football-team/, Accessed 30 Nov 2017

\bibitem{moneyball}
Lewis, Michael. "Moneyball: The Art of Winning an Unfair Game". New York: W.W. Norton, 2003.

\end{thebibliography}