%------------------------------------------------------------------------
% Introduction/Motivation/Objective Section: 
% In this section you should introduce (at a high level) the overall theme of the project, and state clearly what are the goals you are trying to achieve. This section should also clearly convey why this project is important, what is the potential impact (applications, etc).
%------------------------------------------------------------------------

The primary objective of this project is to build a system to predict winning line-ups of basketball players for daily fantasy basketball competitions. A winning line-up is any line-up that, upon being entered into the competition, yields more money than the entry fee (i.e. gains a profit). The goal of the project was to  accomplish this using machine learning. We hypothesized this could be successful based on the assumption that there are hidden relationships between players on the same team, and the players on the opposing team. The project was separated into separate milestones that were intended to collectively allow us to build the final result. These milestones were:
\begin{enumerate}
\item{Learning the necessary material regarding topics in machine learning}
\item{Collecting sufficient amounts of data to allow machine learning to actually take place}
\item{Finding relevant tools and technology to actually implement our final system.}
\end{enumerate}
The importance of this project has two components, one personal and one societal. The personal importance of this project has to do with the team creating it. This project has been, and will continue to be, a valuable learning opportunity. It allows the creators to learn more about data collection, machine learning, software projects, best practices, and engineering design. Machine learning is a field of significant interest to all of us. There is also a societal impact, tied to both the sports and academic communities. If we find that we are able to accurately and consistently predict winning line-ups for fantasy basketball, it may impact the way in which fantasy sports are played by everyone. Rather than rely on intuition, or optimization techniques alone, there may be more movement to use a neural network-based system if it can predict player performances with greater accuracy. This could not only change how fantasy competitions are played, but could be adapted to select which players should actually be played, in real life. Theoretically, a coach could use the same technique, although with a different metric (winning a game instead of maximizing fantasy points) to figure out who to play. Machine learning could help find patterns that we did not know exist. Finally, on the academic side, it could lead to more research on the applications of machine learning to sports betting.
