\subsection{How We Worked as a Team}
In order to facilitate and improve the efficiency of teamwork within our group, we made use of several tools and strategies throughout the semester. For communication within the group, we used the Slack messaging app. For collaboration on code, we made use of git for version control, and github for code reviews. Weekly in-person meetings were had amongst all team members in order to come with fresh project ideas as a group, and to ensure that all of us were on the same page. Weekly in-person meetings with our supervisor were also had for similar reasons, and to ensure that we stayed on track throughout the semester. Without the use of these tools and strategies, the development process for this project would have been much more difficult.

\subsection{Individual Contributions}
Below we show the individual contributions of each person. Note, however, that much work was done as a group, so there are many areas that were worked on collectively by everyone.

\subsubsection{Ege}
\begin{itemize}
  \item Worked on designing the database schema for the database that would house all the data being collected for the project.
  \item Implemented the scrapers that would retrieve the player and match data from stats.nba.com.
\end{itemize}
\subsubsection{Stephen}
\begin{itemize}
  \item Worked on algorithms that compute player scores, both historical and for a given game, and worked on writing scripts to insert given data into database.
  \item Performed data integrity analysis to ensure that all data received made sense, and if something was wrong, sought to find out what was wrong with is and what was missing.
\end{itemize}
\subsubsection{Florence}
\begin{itemize}
  \item Built preliminary neural network that predicts which team will win a given basketball match.
  \item Worked on overall architecture design of three-part prediction system.
\end{itemize}
\subsubsection{Asher}
\begin{itemize}
  \item Worked on scripts to compute player scores, and scripts to connect tables in the database.
  \item Worked on data retrieval code from database to obtain data in a format appropriate for the TensorFlow neural network.
  \item Helped to implement scrapers for some player statistics.
\end{itemize}

\subsection{Evaluation of Teamwork and Difficulties}
The four of us worked very well together as a team and have yet to have any problems thus far in the project. The number of difficulties faced this semester were minimal since we worked so well as a group. We hope to continue this same good work through next semester.
